\subsection{Events}


\subsubsection{Concerts and Convocations}
The Department of Convocations sponsors a wide variety of events including:

\begin{itemize}
	\item chamber music groups
	\item individual virtuoso musicians
	\item various symphony orchestras and ballet troupes
	\item theatrical companies doing musical plays and revues
	\item individual performers
\end{itemize}

Many of the events have ``big names,'' and most are worthwhile.

Near the beginning of fall semester, slick brochures appear around campus describing the coming year's slate of convocations and the season ticket options available (these are usually cheaper; amounting to getting one or two of the tickets free when compared to the single ticket price). If you are buying season tickets, you must decide upon the series you want to buy (there are several and they sometimes change over time) or commit to a number of performances of your own choice. The brochures describing the coming events state which series contains which convocations. Also, several weeks before each event, ads appear in the Exponent (campus newspaper) stating when individual tickets will be sold.

With a student ID, you can buy Convocations tickets at the (lower) student rate. This also applies to season tickets. For further information, go to \url{https://www.purdue.edu/convocations/} or to the ticket office at the north end of the lobby in the Hall of Music or to the ticket windows in Stewart Center, located at the south end of the lobby with the mural.




\subsubsection{Sports}
Purdue is part of the Big 10 conference and people around here go crazy for football and basketball. However, non-revenue sports events at Purdue are rather poorly attended. University fees include an activity fee which entitles students to reduced tickets for sporting events such as football, basketball, and volleyball.

With a student ID, you get reduced price season football tickets. Single game tickets are also available, but in most cases they cannot be purchased at discounted price.



\subsubsection{Movies}
The Purdue Student Union Board (PSUB) regularly schedules film series each semester. The movies are shown on Friday and Saturday evenings in Fowler Hall which is part of the Stewart Center. Show times are usually at 7:00 and 9:30 PM. For PSUB calendar of events, see \url{https://union.purdue.edu/studentevents/}.


