\subsection{Food}


\subsubsection{Campus Food}
If you live in one of the dorms or one of the grad houses, you have a cafeteria available for all your eating needs. The Lawson Computer Science Building, The Purdue Memorial Union, and Stone Hall also have cafeterias which are available to the general public.

The Port - Located in the Lawson Building. You immediately see it when you enter the front door. Breakfast items, fruit, sandwiches, mini-pizzas, soup, salad, coffee, and smoothies can be found here.

Purdue Memorial Union - The Union offers a wide range of food for breakfast, lunch, and dinner at reasonable prices. There is a cafeteria with a variety of cafeteria foods. Purdue students are tax exempt at the cafeteria, so be sure to bring along your Student ID. The Union also serves pizza, ice cream, burgers, and other munchies on the ground floor.

Restaurants surround the campus on every side. Some of the more popular eating establishments are located in Purdue West, The Village and Chauncey Hill Mall, and the area north-east of campus.


\subsubsection{Produce}
In the fall, you can buy one-gallon jugs of apple cider and ten-pound bags of apples (many varieties) at the Purdue Farm. Prices are comparable to those in local grocery stores, but the quality is much higher. Sometimes they also sell pumpkins, squash, and other fall vegetables. The farm is located about 3 miles west on State Road 26 from the Purdue West Shopping Plaza. Watch carefully for signs on the left. Turn off (left) after passing the orchard. The farm is about 1/4 mile on the right.



\subsubsection{University Meat Market}
Purdue offers classes in butchery, and where there's a butcher, there's raw meat. The fruits of the aspiring butchers' labors are sold each Wednesday from 3:00 to 5:30pm and Friday from 12:00 am to 4:30 pm in Smith Hall, room 170. (Smith Hall is on the south side of State St., nearly due south of Matthews Hall. Room 170 is in the west wing of the building.) Most of the common cuts of beef and pork are produced, though not all cuts are available every week. Occasionally, turkey and lamb are also available. As with produce, the prices are comparable to those in local supermarkets, but the quality is outstanding (which is what you will be if you don't get there early and beat the rush). If you need more information about the Boilermaker Butcher Block, call them at 49-48285.





