\subsection{History}

\begin{tcolorbox}[colback=green!5!white,colframe=green!75!black]
	Purdue Computer Science Department is the oldest CS department in the United States!
\end{tcolorbox}

In case you didn't know, Purdue's CS department is the oldest in the country, formally authorized in October 1962. Dr. Sam Conte was the first department head, serving until July 1979, when Dr. Peter Denning took over. Dr. Denning took a position with NASA in June, 1983 at which point Dr. John Rice became department head. After 13 years of distinguished service, Dr. Rice stepped down and returned to teaching. He was succeeded by Dr. Ahmed Sameh who came aboard during the 1996-1997 academic school year. Dr. Susanne Hambrusch, was appointed in the year 2002 and held the position until the summer of 2007. At that point in time Aditya Mathur took over as department head. In June 2012, Dr. Sunil Prabhakar has been appointed Head of the Department of Computer Science after a period of serving as an interim department head.

We are also one of the largest and most highly-rated departments in the country. We received more than 4,000 undergraduate applications for Fall 2017. Currently, 1,708 students are enrolled in the undergraduate program, an all-time high that more than doubles the number of students enrolled just five years ago.

The CS department was originally located in the Math building. In 1985, the CS department moved into a building all to itself. This building was formerly the Memorial Gymnasium. (The Memorial is to a group of Purdue students and alumni who died in a train wreck while traveling to a game). It has been completely renovated to hold us. During the renovation it was rumored that a swimming pool would be left in the basement, but this idea was apparently dropped. Finally, in the fall of 2006, the department moved into our new location, the Lawson Computer Science Building.
